---
title: "Eating Out"
author: "Karina Toribio"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

Is there a relationship between races and how frequently they go out to eat

## There were two years in which the General Social Survey asked about the frequency of eating out.
### Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```
```{r, eval=TRUE}
#race = c("white", "black","other")
GSS <-readstata13::read.dta13(file="GSS1996.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```

# Method

The variable of the study is Cat ~ Num 

# Results

## Descriptive Results

### Numerical Descriptive Results

```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1)
```


### Graphical Descriptive Results

```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata,type="percent")
```

The bar chart suggests that there is a difference in the percentage of races and eating out 

### Inferential Results

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```


# Discussion and Conclusion

Based on the results, we reject the null hypothesis due to the p-value being so small, 0.0008179, concluding that the there is a difference in the frequency of eating out based on race. Therefore, we can conclude that white people go out to eat more than black people and other ethnicites do.

